---
author: "Lorena Pantano"
title: "General templates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pkgdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Adding funding to template

There are two options to add into the templates the funding text
that goes into acknowledgement.

## sourcing from github

You can load the code with devtools, from the remote repository:

```{r load-code, message=FALSE, results='asis'}
devtools::source_url("https://github.com/hbc/hbcABC/raw/master/R/funding.R")
```


## installing hbcABC package

If you install the packate with devtools:

```{r install-code, message=FALSE}
devtools::install_github("hbc/hbcABC")
library(hbcABC)
```

## Adding funding information

Then you can access directly to the functions:

```{r example, results='asis', message=FALSE}
cat(funding_catalyst(), funding_general("LPantano", "RNASeq analysis"))
```

```{r all-functions}
ls("package:hbcABC")[grepl("funding", ls("package:hbcABC"))]
```

Some of the `funding_*` functions need some arguments, like `author`, and `service`.

You can look for documentation with `?funding_*`.

