---
author: "Lorena Pantano"
title: "SingleCell RNAseq templates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pkgdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Single cell templates

Please, contribute with your improvements. I am sure you have something to add.

```{r echo = FALSE}
root = "https://github.com/hbc/hbcABC/tree/master/inst/rmarkdown/Rscripts/singlecell"
# root = "../../inst/rmarkdown/Rscripts/singlecell"
dir.create("reports")
```


## QC

`simple_qc_single_cell` is a template to run a fast QC with ggplot code
to modify the plots as needed.

To create the template, use the Rstudio menu as for any other template or:

```{r copy-qc}
source = file.path(system.file("rmarkdown", package="hbcABC"),
          "templates", "sinple_qc_single_cell",
          "skeleton",
          "skeleton.rmd")
file.copy(source, "reports/simple_qc_sc.rmd")
```

The next step is to run the normalization, scaling and clustering that are high
demand in computation time and memory.

## Clustering with Seurat

To run this analysis please read the documentation from [our knowledgebase repo](https://github.com/hbc/knowledgebase/blob/master/research/scrnaseq/Single-Cell.md)

If you get to have these two objects:

* seurat_pre_regress.rds
* seurat_tsne.rds

These objects will be used by `seurat_clustering_single_cell` to perform
best practices as described by seurat tutorial.

```{r seurat-clustering}
source = file.path(system.file("rmarkdown", package="hbcABC"),
          "templates", "seurat_clustering_single_cell",
          "skeleton",
          "skeleton.rmd")
file.copy(source, "reports/seurat_clustering.rmd")
```


```{r remove, echo = FALSE}
system("rm -rf reports")
system("rm -rf *.r")
```

